Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-01 overleaf/results.tex
add updated graphs
add error bars to the graphs

We run all experiments 5 times and report average values of various metrics. Note that standard deviation in all observations was at most 1\% of the mean value, therefore the accuracy of the results is not effected by the relatively fewer runs.

@@

\begin{figure*}[htbp]
\centering
\include{graphs/all-hist-OnlineSetupTimesec}
\caption{Circuit Evaluation Time (Setup + Online) of Benchmarks}
\label{fig:graph_all_online_setup}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/all-hist-CommunicationMiB}
\caption{Communication Size of Benchmarks}
\label{fig:graph_comm_size_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/all-hist-CircuitGenerationTimesec}
\caption{Circuit Generation Time of Benchmarks}
\label{fig:graph_circ_gen_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/all-hist-TotalGates}
\caption{Number of Gates of Benchmarks}
\label{fig:graph_total_gates}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/all-hist-OnlineTimesec}
\caption{Online Time of Benchmarks}
\label{fig:graph_online_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/all-hist-SetupTimesec}
\caption{Setup Time of Benchmarks}
\label{fig:graph_setup_time}
\end{figure*}

>>>>

We run all experiments 5 times and report average values of various metrics. Note that standard deviation--shown as errorbar on top of the bars in the graphs--in all observations was at most 4.5\% of the mean value, therefore the accuracy of the results is not effected by the relatively fewer runs.

@@

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-OnlineSetupTimesec}
\caption{Circuit Evaluation Time (Setup + Online) of Benchmarks}
\label{fig:graph_all_online_setup}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-CommunicationMiB}
\caption{Communication Size of Benchmarks}
\label{fig:graph_comm_size_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-CircuitGenerationTimesec}
\caption{Circuit Generation Time of Benchmarks}
\label{fig:graph_circ_gen_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-TotalGates}
\caption{Number of Gates of Benchmarks}
\label{fig:graph_total_gates}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-OnlineTimesec}
\caption{Online Time of Benchmarks}
\label{fig:graph_online_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\include{graphs/lan/all-hist-SetupTimesec}
\caption{Setup Time of Benchmarks}
\label{fig:graph_setup_time}
\end{figure*}
